\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-26 OaklandSubmission/impl.tex
minor

\section{Implementation}
\label{sec:impl}
We discuss some  implementation details of \tool.
The  \tool compiler is written in Python and
compiles each of our benchmarks in under a second to C++ code that
makes calls to the ABY
library~\cite{aby}. We use the default ABY configuration for our
experiment \footnote{We set the security parameter to 128 and use OT
extension-based arithmetic multiplication triples generation.}. ABY
provides multi-threading support (for the offline phase of the
protocol), we leverage the support and use at most four threads in our
evaluation.

@@

Secure code partitioning currently requires a manual step.
In particular, the developer needs to decompose a program $P$ into
$P_1||\ldots||P_k$ manually (Section~\ref{sec:pipe}). Then \tool
generates $Q_1||\ldots||Q_k$ (the sub-programs with appropriate
wrappers) automatically.
Automating the decomposition step requires an analysis that can 
statically estimate the resource usage of an \tool program. We leave
the construction of such an analysis as future work.

@@

The compilation rules of Figure~\ref{fig:compile} can introduce
repeated coercions from arithmetic to
boolean and vice versa.
The \tool implementation performs several optimizations to reduce
these coercions.
For example, on each coercion, \tool memorizes the pair of arithmetic
share and boolean share involved in the coercion. 
\tool invalidates such pairs when the variables corresponding to the
shares are overwritten by assignments. 
In subsequent coercions, \tool  reuses valid pairs (if available)
instead of recomputing them afresh.

>>>>

\section{Implementation}
\label{sec:impl}
We discuss some  implementation details of \tool.
The  \tool compiler is written in Python and
compiles each of our benchmarks in under a second to C++ code that
makes calls to the ABY
library~\cite{aby}. We use the default ABY configuration for our
experiment \footnote{We set the security parameter to 128 and use OT
extension-based arithmetic multiplication triples generation.}. ABY
provides multi-threading support (for the offline phase of the \mpc
protocol); we leverage the support and use at most four threads in our
evaluation.

@@

%Moved this to Section 4 since P_i and Q_i are ill defined here
%Secure code partitioning currently requires a manual step.
%In particular, the developer needs to decompose a program $P$ into
%$P_1||\ldots||P_k$ manually (Section~\ref{sec:pipe}). Then \tool
%generates $Q_1||\ldots||Q_k$ (the sub-programs with appropriate
%wrappers) automatically.
%Automating the decomposition step requires an analysis that can 
%statically estimate the resource usage of an \tool program. We leave
%the construction of such an analysis as future work.

@@

The compilation rules of Figure~\ref{fig:compile} can introduce
repeated coercions from arithmetic to
boolean and vice versa.
The \tool implementation performs  the standard ``common subexpression elimination"
optimization to reduce these coercions.
On each coercion, \tool memorizes the pair of arithmetic
share and boolean share involved in the coercion. 
\tool invalidates such pairs when the variables corresponding to the
shares are overwritten by assignments. 
In subsequent coercions, \tool  reuses valid pairs (if available)
instead of inserting code to recompute them afresh.
